% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

Firstly, my deepest appreciation (and sincerest apologies) go to my two supervisors; Dr. Nima Razavi-Ghods and Dr. Will Handley for their continued support, guidance and patience. I know I could not have been the easiest person to work with, and I am eternally grateful to have been taken on as a student by them.

Thanks to my dearest parents Thomas and Solon; I can’t believe how lucky I am to be their son. I wouldn’t trade it for the world.

Thanks to my loving family; Andrew, Ben, Dick, Lily, Matthew, May, Rachel, Solia and Susie, for waiting so patiently for me, and to my cherished grandmothers, Camila and Betty, for their everlasting love.

I truly could not have done this without my darling Sabrina. My heartfelt gratitude for putting up with me dear. A very special thanks to Waldemar and Martina for opening up their home to me, especially during the most critical and difficult periods of thesis writing. And thanks to Martha for the endless support and affection.

I am honoured by the fellowship and assistance of Dr. William Barker. Appreciation goes to Dr. Florian Lienhard for being the best office mate anyone could ask for, and to Prof. Dave Green for being the best office neighbour anyone could ask for. I also wish to acknowledge Steven Carey and John Ely whose hard work and knowledge were integral to this project, for which I am truly grateful. I am very grateful to my group as well. Dr. Dominic Anstey generously provided much of his time and expertise teaching me the mathematical background of which this work is based. Dr. Harry Bevins provided an ideal to strive for. Dr. John Cumner listened to every single one of my rants and helped me pull through on my worst days. Thomas Gessey-Jones patiently and thoroughly answered all of my questions regardless of how trivial they were or how many times I walked into his office unannounced. Thanks goes to Samuel Leeny for all the support and lunchtime chats. I also wish to thank Kilian Scheutwinkel for all of the advice and encouragement. It really meant a lot to me.

Thanks goes to Prof. Patrick Carrazana for believing in me, to Prof. Richard Saunders for his boundless wisdom and to Dr. Thomas Feggeler for the continued professional advice. I am truly grateful for the guidance of Dr. Christopher O’Grady, Dr. Monarin Uervirojnangkoorn and Prof. Stefano Profumo. I would not be here without them. For changing how I see the world, I would like to thank Prof. Richard Mitchell and for starting me on this journey I would like to acknowledge Mr. Steve Ratto. Mrs. Katie Ward showed me endless kindness for which I am honoured as well. I am indebted to so many wonderful teachers who taught, supported and encouraged me including; Prof. Steven Ritz, Prof. George Brown, Prof. Enrico Ramirez‑Ruiz, Dr. Adriane Steinacker, Mr. Arron Apperson, Mr. Nate Kundin, Mr. David Martin, Mr. Asif Rahman, Mr. Rich Serrao, and Mrs. Cristina Trujillo.

I am grateful to Dr. Anas Al Rawi, Prof. Paul Rimmer, Mr. Anthony Djedi and Mr. Steven Brereton for their pastoral and professional support and to all my treasured friends met along the way; Khalid Aleem, Morgan Dang, Joe Ferris, Khalen Hudson, Perman Jorayev, Edii Lam, Liam Lau, James Luis, Derek Ngoon, Michael O'Donnghaile, Peter Pedersen, and Matt Wang. Franklin, Derek and Arun were the most genuine of friends even when I wasn’t, and I could not have done any of this without Will Mandell.

I give thanks to John and Michelle Bentley for their sincere kindness and belief in me. I would also like to acknowledge the colleagues we’ve lost; Prof. Richard Hills and Dr. David Sun who challenge us to be the best of scientists and of course, my beloved auntie Solane.

And finally, thanks goes to those who inspired me to undertake this endeavour in the first place; Dr. Neil deGrasse Tyson, Prof. Brian Greene, Prof. Brian Cox and Prof. Michio Kaku.

\end{acknowledgements}
